MLH1 Data Report

### 2019-08-15 doc/Main_Report.rmd
put in the new Rdata file to main report

---
title: "MLH1 Data Report"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="data/MLH1/MLH1_data_setup.RData")
```

@@

-  *Report basic statistics of results and to help keep track of the number of images for each category and mouse*

@@

These are the tables for the number of mice and cells which have been quantified. (what is in the 'other' category?)

@@

```{r first.boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
              "WSB", "PWD","MSM","KAZ","CAST","HMI","SPRET","SPIC", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey" )) +
 ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+5))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" )) +
  ylim( c( (min(MLH1_data$adj_nMLH1.foci)-3), (max(MLH1_data$adj_nMLH1.foci)+5)) )

@@

After taking the data from 2 highest cell quality, some but not all mouse means converge.

@@

```{r high qual, fig.caption="boxplots of MLH1 distributions", fig.height=5, fig.width=5, echo=FALSE, warnings=FALSE}

@@

```{r, scatter plots of nMLH1 by score, echo=FALSE, fig.cap="caption"}
#make lattice / plots seperated by strain and sex
#facet

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is 
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)
n
```

#### Power Calculations

Main questions to address:

 > *How many cells per mouse should be sampled?*

 > *How many mice per strain should be sampled?*

Outline discription of the loop for comparing sample size effects

i) take ~100 independant samples of total images across different sample sizes (10%, 25%, 50%, 75%, 90%)
ii) then run t.tests across those samples, and report the p value 
iii) make a table of the p values for these sample permutations
iv) plot the p values or mean p values across sample sizes

Currently this section is under construction.

```{r, include=FALSE}
#passed_mice_data <- MLH1_data[MLH1_data$mouse %in% passed_mice, ]
#non_passed_mice_data <- MLH1_data[MLH1_data$mouse %in% not_passed, ]

#make a column to mark if observation comes from passed or not passed mouse
#turn this into boxplot and sort the category order, otherwise it's hard to any patterns
#sc <- qplot(mouse, nMLH1.foci,  colour = category, data = non_passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

#sc <- qplot(mouse, nMLH1.foci,  colour = category, data = passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

# not working not sure of the purpose
#count =1
#for(i in MLH1_data$file.name){
#  templist= strsplit(i, split="_")[[1]]
#  if(MLH1_data$mouse %in% passed_mice) 
#  MLH1_data$mouse[count] <- c
#  count= count +1
#}
```

>>>>

---
title: "MLH1 Data Report"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")
load(file="data/MLH1/MLH1_data_setup_8.15.19.RData")

@@

-  Report basic statistics of results and to help keep track of the number of images for each category and mouse

@@

These are the tables for the number of cells and mice which have been quantified.
The 'Other' are F1 crosses.

@@

```{r first.boxplots, echo=FALSE, fig.align='center'}
#what?
#MLH1_data <- MLH1_data[MLH1_data$strain]

#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEW","WSB",
              "PWD","MSM","MOLF","CZECH","SKIVE",
              "KAZ","TOM","AST",
              "CAST","HMI","SPRET","SPIC", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])

#don't know why this won't do the right order...
#set the order of another column, based on another variable (so that when)

@@

#try this for ordering
#MLH1_data[order(MLH1_data$strain), ]

#can't re-order the miceagg
ff <- ggplot(MLH1_data[order(MLH1_data$strain), ], 
             aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue", "coral4","coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey", 
        "grey","grey","grey",  "grey","grey","grey" )) +
 ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+5)) + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by strain") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" )) +
  ylim( c( (min(MLH1_data$adj_nMLH1.foci)-3), (max(MLH1_data$adj_nMLH1.foci)+5)) )

@@

### Distributions of MLH1 counts

@@

### Histograms of Mouse Ages

```{r age.hists, echo=FALSE}
#meta.data.file2 = read.csv("~./MLH1repo/data/MouseMetaData61119.csv", header = TRUE)
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)
meta.data.file2 <- meta.data.file2[!(is.na(meta.data.file2$mouse)|meta.data.file2$mouse==""),] #375

meta.data.file2$DOB <- as.Date(meta.data.file2$DOB, format= "%m/%d/%Y")#%Y 2000, %y '18,

#make Mouse meta data work
MouseMetaData.wrkin <- meta.data.file2[,c(1,4)]
colnames(MouseMetaData.wrkin) <- c("mouse", "DOB")
MouseMetaData.wrkin <- MouseMetaData.wrkin[!(is.na(MouseMetaData.wrkin$mouse)|MouseMetaData.wrkin$mouse==""),]

#do this for the mouse table instead of the MLH1 table
MLH1.imprv <- merge(MLH1_data, MouseMetaData.wrkin)#don't apply the all parameters

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
MLH1.imprv <- add_euth_date(MLH1.imprv)
#
MLH1.imprv$euth.date2 <- MLH1.imprv$euth.date
MLH1.imprv$euth.date <- as.Date(as.character(MLH1.imprv$euth.date2), format='%d%b%y')

MLH1.imprv <- add_age(MLH1.imprv)

#remove mice that are older than 20 weeks
MLH1.imprv.male <- MLH1.imprv[MLH1.imprv$sex == "male", ]
MLH1.imprv.male <- MLH1.imprv.male[MLH1.imprv.male$age.weeks < 20, ]

pp <- ggplot(MLH1.imprv.male, aes(age.weeks))+geom_histogram()+facet_wrap(~category)+ggtitle("Age Distributions")
pp

#what is this meta.data.file?
#meta.data.file2 <- add_strain(meta.data.file2)
#meta.data.file2 <- add_sex(meta.data.file2)
#meta.data.file2 <- add_category(meta.data.file2)
#meta.data.file2 <- add_euth_date(meta.data.file2)
#meta.data.file2 <- add_age(meta.data.file2)

#qq <- ggplot(meta.data.file2[meta.data.file2$sex == "male",], aes(age.weeks))+geom_histogram()+facet_wrap(~category)+ggtitle("recorded ages of dissected mice")
#qq

#### Assesment of Quality Scores

```{r high qual, fig.caption="boxplots of MLH1 distributions", fig.height=5, fig.width=5, echo=FALSE, warnings=FALSE, include=FALSE}

@@

```{r, scatter plots of nMLH1 by score, echo=FALSE, fig.cap="MLH1 means across quality scores"}
#make lattice / plots seperated by strain and sex
#facet

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is TOO big
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)
